---
title: "lab report"
author: "Wayne Wu"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 17.05.25 / T

* Cell culturing
    + SHSY cells
        + 10 plates for differentiation: RA day 3
        + 30 plates for mito extraction: confluency at ~10%
    + 293T KO cells
        + Split, with half stored as frozen stock and half to new plate
        + Transfection tommorw once sequence is confirmed




## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
